Open Data for _Crime and Place_ Research: A Practical Guide in R.

### 2020-11-18 manuscript.Rmd
revisions update

The drive towards transparency and scrutiny of public information is further enhanced by an increasing need for replication - a hallmark for open science research practice. Opening up datasets used in criminology publications and wider social sciences fosters and facilitates a culture of replication [@pridemore2018replication]. As such, open data fits into the wider discourse around transparency, open review and open scrutiny, which (in time) may even become a policy requirement irrespective of the research field or the source of funding [@vuong2017open]. Increasingly, researchers are making use of online repositories for their papers (e.g. https://arxiv.org/), data (e.g. https://www.ukdataservice.ac.uk/deposit-data), code (e.g. https://github.com/), or whole projects (e.g. https://osf.io/) all in the name of transparency and replication. These are guidelines and tools worth considering, not just when conducting analysis on secondary data sources, but also collecting and sharing your own data.

@@

This chapter has sought to introduce open data as a novel, growing and invaluable tool in crime and place research through a review of key fundamentals and a substantive demonstration within R. We have defined open data, and outlined some key types of open information available, along with their respective strengths and weaknesses. An important component of this review has been to encourage an engaged and critical research approach to using open data. Open data is both a rich resource of dependent and independent variables for researching the geography of crime, and an interesting research topic in and of itself as a tool for providing insight overlooked by traditional data sources. The suppmentary material contained a practical exercise in which we accessed different sources of open data in order to explore crime concentrations at London Underground stations on the Jubilee line: police-recorded crime data via a direct download from a public sector website, transport data via directly querying a public sector API, hosted by Transport for London, and the equivalent transport data retrieved from a crowdsourced database, Open Street Map, using an API wrapper. Minor discrepancies in the geographic location of underground stations in each open data source painted two starkly different stories about the volume and concentration of crime occurring on the line. The demonstration highlighted both the power of open data and the need to critically engage with sources.

>>>>

The drive towards transparency and scrutiny of public information is further enhanced by an increasing need for replication. This is a key component of open science: transparent, reusable, reproducible and accessible research practices. Opening up datasets used in criminology publications and wider social sciences fosters and facilitates a culture of replication [@pridemore2018replication]. As such, open data fits into the wider discourse around transparency, open review and open scrutiny, which (in time) may even become a policy requirement irrespective of the research field or the source of funding [@vuong2017open]. Increasingly, researchers are making use of online repositories for their papers (e.g. https://arxiv.org/), data (e.g. https://www.ukdataservice.ac.uk/deposit-data), code (e.g. https://github.com/), or whole projects (e.g. https://osf.io/) all in the name of transparency and replication. These are guidelines and tools worth considering, not just when conducting analysis on secondary data sources, but also collecting and sharing your own data.

@@

This chapter has sought to introduce open data as a novel, growing and invaluable tool in crime and place research through a review of key fundamentals and a substantive demonstration within R. We have defined open data, and outlined some key types of open information available, along with their respective strengths and weaknesses. An important component of this review has been to encourage an engaged and critical research approach to using open data. Open data is both a rich resource of dependent and independent variables for researching the geography of crime, and an interesting research topic in and of itself as a tool for providing insight overlooked by traditional data sources. The supplementary material contained a practical exercise in which we accessed different sources of open data in order to explore crime concentrations at London Underground stations on the Jubilee line: police-recorded crime data via a direct download from a public sector website, transport data via directly querying a public sector API, hosted by Transport for London, and the equivalent transport data retrieved from a crowdsourced database, Open Street Map, using an API wrapper. Minor discrepancies in the geographic location of underground stations in each open data source painted two starkly different stories about the volume and concentration of crime occurring on the line. The demonstration highlighted both the power of open data and the need to critically engage with sources.

### 2020-11-18 supplementary_materials.Rmd
revisions update

For this exercise, we are going to use British Transport Police data, a force which operates on railways and light-rail systems across the country, for the month of January in 2020. Select the time period using the dropdown menus, the force using the tickboxes, and then generate and download the file.

@@

In the documentation, there is a section called 'API area' which offers some guidance on the types of data available. Scroll down and find the example called _Stops_. You will see that this call returns information on stops for buses or London Underground lines, and there are two examples (bus route 24 and the Bakerloo line). Copy their demonstration URL for the bakerloo line (https://api.tfl.gov.uk/line/bakerloo/stoppoints) and paste it into your web browser. When you visit this page, you should see something like Figure 1.

@@

We can now easily visualize this data (see Figure 2) using the `ggplot2` package, which is compatible with `sf` objects.

@@

We can now plot the Open Street Map station points, which are already spatial, over these station locations pulled from the TfL API, to see how the two datasets compare (see Figure 3).

@@

We can then visualize these counts and compare the two sources of data by coloring in our buffers according to the crime count (see Figure 4). Note that we arrange the plots using syntax available using the `patchwork` package, and set the scales to be comparable using the `lim` argument within `scale_color_viridis_c()`.

@@

We can explore Stratford station as a potential crime hotspot using some of the skills we have learnt so far. One useful first step might to visualize the built environment around the station, along with the crime buffers from Open Street Map and TfL respectively, and the crime locations themselves (see Figure 5). This way, we might find out why the TfL buffer is failing to capture any crimes, while the Open Street Map buffer is capturing an apparent crime hotspot. In doing so, it is worth remembering that crime locations in open police data are approximations of the real geography in order to ensure anonymity.

@@

>>>>

For this exercise, we are going to use British Transport Police data, a force which operates on railways and light-rail systems across the country, for the month of January in 2020. Select the time period using the dropdown menus, the force using the tickboxes (see Figure 1), and then generate and download the file.

@@

In the documentation, there is a section called 'API area' which offers some guidance on the types of data available. Scroll down and find the example called _Stops_. You will see that this call returns information on stops for buses or London Underground lines, and there are two examples (bus route 24 and the Bakerloo line). Copy their demonstration URL for the bakerloo line (https://api.tfl.gov.uk/line/bakerloo/stoppoints) and paste it into your web browser. When you visit this page, you should see something like Figure 2.

@@

We can now easily visualize this data (see Figure 3) using the `ggplot2` package, which is compatible with `sf` objects.

@@

We can now plot the Open Street Map station points, which are already spatial, over these station locations pulled from the TfL API, to see how the two datasets compare (see Figure 4).

@@

We can then visualize these counts and compare the two sources of data by coloring in our buffers according to the crime count (see Figure 5). Note that we arrange the plots using syntax available using the `patchwork` package, and set the scales to be comparable using the `lim` argument within `scale_color_viridis_c()`.

@@

We can explore Stratford station as a potential crime hotspot using some of the skills we have learnt so far. One useful first step might to visualize the built environment around the station, along with the crime buffers from Open Street Map and TfL respectively, and the crime locations themselves (see Figure 6). This way, we might find out why the TfL buffer is failing to capture any crimes, while the Open Street Map buffer is capturing an apparent crime hotspot. In doing so, it is worth remembering that crime locations in open police data are approximations of the real geography in order to ensure anonymity.

@@

[INSERT FIGURE 6 HERE]
